Translation Elicitation: Report

### 2022-10-28 docs/index.Rmd
Add questionnaire data and analyses, and change reports to Quarto

```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# import data
tar_load_globals()
tar_load_all()

@@

```{r stimuli-coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE,  include=FALSE}

stimuli_coded <- stimuli %>% 
  mutate(test_language = ifelse(group=="spa-ENG", "Spanish", "Catalan"))
```

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
  select(group, word1, frequency, frequency_zipf, pthn, lv) %>% 
  group_by(group) %>% 
  summarise_at(
    vars(frequency:lv), 
    list(
      median = ~median(., na.rm = TRUE),  
      sd = ~sd(., na.rm = TRUE)
    )
  ) %>%
  gt(rowname_col = "group") %>% 
  tab_header(
    title = md("Table 1"),
    subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
  ) %>% 
  tab_source_note(
    md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
  ) %>% 
  fmt_number(frequency_median:pthn_sd) %>%
  fmt_percent(matches("lv")) %>% 
  tab_spanner(md("**Freq. (million)**"), c("frequency_median", "frequency_sd")) %>% 
  tab_spanner(md("**Freq. (Zipf)**"), matches("frequency_zipf")) %>% 
  tab_spanner(md("***PTHN***"), matches("pthn")) %>% 
  tab_spanner(md("**Levenshtein**"), matches("lv")) %>% 
  cols_label(
    frequency_median = md("Median"),
    frequency_sd = md("*SD*"),
    frequency_zipf_median = md("Median"),
    frequency_zipf_sd = md("*SD*"),
    pthn_median = md("Median"),
    pthn_sd = md("*SD*"),
    lv_median = md("Median"),
    lv_sd = md("*SD*")
  ) %>% 
  summary_rows(
    columns = c(matches("median"), -matches("lv")),
    fns = list(
      Median = "median",
      SD = "sd"
    )
  ) %>% 
  summary_rows(
    columns = matches("lv"),
    fns = list(
      Median = "median",
      SD = "sd"
    ), formatter = fmt_percent
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_stub_grand_summary()
  ) %>% 
  tab_style(
    style = cell_borders(sides = c("left", "right"), color = "white"),
    locations = list(
      cells_body(), cells_row_groups(), cells_column_spanners(), 
      cells_stub(), cells_stub_grand_summary(), cells_source_notes(),
      cells_column_labels(), cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(cell_text(align = "left", size = "medium"), cell_borders(sides = "all", color = "white")),
    locations = cells_stub()
  ) %>% 
  tab_style(
    style = cell_text(align = "center", size = "medium", weight = "normal", style = "normal"),
    locations = list(cells_column_spanners(), cells_column_labels())
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:9)
  ) %>% 
  as_raw_html()

@@

```{r stimuli-frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  distinct(
    test_language,
    word1,
    .keep_all = TRUE
  ) %>% 
  left_join(count(., test_language, name = "n_total")) %>% 
  mutate(test_language = paste0(test_language,  " (N = ", n_total, ")")) %>% 
  ggplot(
    aes(
      frequency_zipf, 
      fill = test_language
    )
  ) +
  facet_wrap(~test_language, ncol = 1) +
  geom_histogram(
    bins = 25,
    colour = "white"
  ) +
  labs(
    x = "Lexical frequency (Zipf score)\nExtracted from CLEARPOND database", 
    y = "# trials", 
    fill = "Test language"
  )  +
  scale_y_continuous(breaks = seq(0, 12, 2)) +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

```{r stimuli-pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(count(., test_language, name = "n_total")) %>% 
  mutate(test_language = paste0(test_language,  " (N = ", n_total, ")")) %>% 
  count(test_language, pthn) %>% 
  ggplot(aes(reorder(as.factor(pthn), -n), n, fill = test_language)) +
  facet_wrap(~test_language, ncol = 1) +
  geom_col(position = position_dodge()) +
  labs(x = "# Phonological neighbours with higher lexical frequency\nExtracted from CLEARPOND database", y = "# trials", fill = "Test language") +
  theme(
    legend.position = "none",
    panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
  )

@@

```{r stimuli-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli_coded %>% 
  left_join(count(., group, name = "n_total")) %>% 
  mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
  ggplot() +
  aes(
    x = group, 
    y = lv,
    fill = group,
    colour = group
  ) +
  geom_violin() +
  geom_point(
    shape = 1,
    stroke = 1, 
    position = position_jitter(width = 0.1), 
    colour = "black", 
    alpha = 0.25
  ) +
  geom_boxplot(
    colour = "black", 
    fill = "white",
    width = 0.1, 
    size = 0.75
  ) +
  labs(
    x = "Group", 
    y = "Phonological Leveshtein distance\n(corrected for string length)",
    fill = "Test language"
  ) +
  scale_y_continuous(
    labels = scales::percent
  ) +
  theme(
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      colour = "grey",
      linetype = "dotted"
    )
  )

@@

@@

medians <- stimuli %>% 
  group_by(group) %>% 
  summarise(
    pthn_median = median(pthn),
    pthn_sd = sd(pthn),
    frequency_zipf_median = median(frequency_zipf),
    frequency_zipf_sd = sd(frequency_zipf),
    lv_median = median(lv),
    lv_sd = sd(lv)
  )

# frequency
stimuli %>% 
  ggplot() + 
  aes(
    x = frequency_zipf,
    fill = group
  ) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = frequency_zipf_median-frequency_zipf_sd,
      xmax = frequency_zipf_median+frequency_zipf_sd, 
      ymin = -Inf,
      ymax = Inf, 
      fill = group
    ),
    inherit.aes = FALSE,
    alpha = 0.15
  ) +   
  geom_histogram(
    bins = 20,
    colour = "white"
  ) +
  geom_vline(
    data = medians, 
    aes(
      xintercept = frequency_zipf_median,
      group = group
    ), 
    colour = "black",
    size = 0.5,
    linetype = "dashed"
  ) + 
  geom_text(
    data = medians, 
    aes(
      label = "Median ± SD", 
      x = frequency_zipf_median+1.25,
      y = 13
    ), 
    size = 3
  ) +
  geom_curve(
    data = medians, 
    aes(
      x = frequency_zipf_median+0.85, 
      xend = frequency_zipf_median+0.1,
      y = 12, 
      yend = 11
    ),
    arrow = arrow(length = unit(0.2, "cm")),
    curvature = -0.25,
    colour = "grey30"
  ) +
  labs(
    x = "Lexical frequency (Zipf)", 
    y = "Number of trials", 
    title = "Frequency\n(stimuli translations)\n"
  ) +

  # PTHN
  stimuli %>% 
  count(group, pthn) %>% 
  ggplot(
    aes(
      x = pthn, 
      y = n,
      fill = group
    )
  ) + 
  facet_wrap(~group, ncol = 1) + 
  geom_rect(
    data = medians, 
    aes(
      xmin = 0, 
      xmax = pthn_median+pthn_sd, 
      ymin = -Inf, 
      ymax = Inf,
      fill = group
    ), 
    inherit.aes = FALSE, 
    alpha = 0.15
  ) +   
  geom_col(colour = "white") + 
  geom_vline(
    data = medians, 
    aes(
      xintercept = pthn_median,
      group = group
    ), 
    colour = "black", 
    size = 0.5,
    linetype = "dashed"
  ) + 
  labs(
    x = "PTHN", 
    y = "Number of trials", 
    title = "Higher-frequency neighbours\n(stimuli translations)\n"
  ) +

@@

  plot_layout(guides = "collect") &
  plot_annotation(tag_levels = "A") &
  scale_fill_manual(
    values = c("#1A85FF", "#ff2976", "#FFC20A"), 
    na.translate = FALSE
  ) &
  theme(legend.position = "none")

@@

participants_coded %>% 
  filter(valid_participant=="Valid") %>% 
  select(
    participant_id, 
    group, 
    n,
    n_valid
  ) %>%
  mutate(valid_prop = n_valid/n) %>% 
  ggplot() +
  aes(
    x = valid_prop, 
    fill = group,
    colour = group
  ) + 
  facet_wrap(~group, ncol = 1) +
  geom_histogram() +
  geom_rug() +
  labs(
    x = "Valid trials (%)",
    y = "N participants",
    fill = "Group",
    colour = "Group"
  ) +
  scale_x_continuous(labels = percent) +
  theme(
    legend.title = element_blank(),
    legend.position = "none",
    axis.title.x = element_blank(),
    panel.grid.major.y = element_line(
      linetype = "dotted", 
      colour = "grey"
    )
  )
```

@@

participants_valid %>% 
  count(group, l2, .drop = FALSE) %>% 
  mutate(
    l2 = case_when(
      l2=="Alemã\u0081n" ~ "German",
      l2=="Francã\u2030s" ~ "French",
      l2=="Cuã\u0081l" ~ "Missing",
      TRUE ~ l2
    ),
  ) %>% 
  left_join(
    count(
      participants_valid, 
      group, 
      name = "n_total"
      )
    ) %>% 
  mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
  ggplot() +
  aes(
    group,
    n,
    fill = l2
  ) + 
  facet_wrap(
    ~group, 
    ncol = 1,
    scales = "free_y"
  ) +
  geom_col(position = position_fill()) +
  labs(
    x = "L2", 
    y = "# participants", 
    fill = "L2"
  ) +
  scale_y_continuous(labels = percent) +
  coord_flip() +
  theme(
    legend.position = "top",
    legend.title = element_blank(),
    strip.text = element_blank(),
    panel.grid = element_blank(),
    axis.text.x = element_text(angle = 90),
    axis.title.y = element_blank()
  )

@@

```{r responses_coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
responses_coded <- responses %>% 
  # typos are considered correct responses
  mutate_at(vars(group), as.factor) %>% 
  # center predictors
  mutate_at(
    vars(lv_std, pthn_std, frequency_zipf_std),
    function(x) scale(x, center = TRUE, scale = TRUE)[,1]) %>% 
  # impute missing data
  as_tibble() %>% 
  arrange(group, word)
```

@@

model_loos %>% 
  as.data.frame() %>% 
  rownames_to_column("model") %>% 
  arrange(desc(elpd_loo)) %>% 
  select(
    model,
    matches("elpd_loo"),
    matches("looic"),
    matches("diff")
  ) %>%
  mutate(model = str_replace(model, "fit_", "Model ")) %>% 
  mutate_all(~ifelse(. == 0, NA, .)) %>% 
  gt(rowname_col = "model") %>% 
  tab_header(
    title = md("Table 2"),
    subtitle = md("Model performance and comparison using leave-one-out cross-validation")
  ) %>% 
  tab_source_note(
    md("*Note*. Outcomes of the leave-one-out cross-validation procedure. Each row indicates the values of the expected log-predicted density (*ELPD*), leave-one-out information creterion (*LOO-IC*), and the difference in *ELPD* (*LOO-diff*) between each model and the inmediately simpler model. Each value is accompanied by a standard error (*SE*) indicating the uncertainty of its estimate.")
  ) %>% 
  fmt_missing(everything(), missing_text = "-") %>% 
  fmt_number(2:7) %>% 
  cols_label(
    model = md("**Model**"),
    looic = md("***LOO<sub>IC</sub>***"),
    se_looic = md("***SE*<sub>IC</sub>**"),
    elpd_loo = md("***LOO<sub>ELPD</sub>***"),
    se_elpd_loo = md("***SE***"),
    elpd_diff = md("***LOO<sub>diff</sub>***"),
    se_diff = md("***SE<sub>diff</sub>***")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", weight = "bold", size = "medium"),
    locations = cells_title(groups = "title")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium", style = "italic"),
    locations = cells_title(groups = "subtitle")
  ) %>% 
  tab_style(
    style = cell_text(align = "left", size = "medium"),
    locations = cells_source_notes()
  ) %>% 
  tab_style(
    style = list(
      cell_borders(
        sides = c("left", "right"), 
        color = "white"
      ),
      cell_text(
        align = "center"
      )
    ),
    locations = list(
      cells_body(), 
      cells_row_groups(), 
      cells_column_spanners(), 
      cells_stub(),
      cells_source_notes(),
      cells_column_labels(),
      cells_stubhead()
    )
  ) %>% 
  tab_style(
    style = list(
      cell_text(align = "left", size = "medium"), 
      cell_borders(sides = "all", color = "white")
    ),
    locations = list(
      cells_stub(), 
      cells_source_notes()
    )
  ) %>% 
  tab_style(
    style = cell_text(
      align = "center", 
      size = "medium",
      weight = "normal",
      style = "normal"
    ),
    locations = list(
      cells_column_spanners(),
      cells_column_labels()
    )
  ) %>% 
  tab_style(
    style = cell_borders(sides = "all", color = "white"),
    locations = cells_body(columns = 1:7)
  ) %>% 
  tab_style(
    style = cell_borders(sides = "top", color = "white"),
    locations = cells_body(columns = 1:7)
  ) %>% 
  as_raw_html()

@@

coefs <- fixef(fit_6) %>% 
  as.data.frame() %>% 
  rownames_to_column("variable") %>% 
  clean_names() %>% 
  mutate_at(
    vars(estimate:q97_5), 
    ~ifelse(
      variable=="Intercept",
      inv_logit_scaled(.),
      ./4
    )
  )

str_repl <- c(
  "Intercept" = "Intercept",
  "frequency_zipf_std" = "Frequency\n[+1 SD]",
  "pthn_std:lv_std" = "PTHN \u00d7 Levenshtein", 
  "lv_std:groupeng_spa" = "Levenshtein \u00d7 Group 1",
  "lv_std:groupcateng_spaeng" = "Levenshtein \u00d7 Group 2",
  "lv_std" = "Levenshtein\n[+1 SD]",
  "pthn_std" = "PTHN\n[+1 SD]",
  "groupeng_spa" =  "Group 1\n[ENG-* vs. cat-SPA]",
  "groupcateng_spaeng" = "Group 2\n[cat-ENG vs. spa-ENG]"
)

>>>>

```{r prepare, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# import data
tar_load_all()

@@

```{r stimuli-table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

stimuli %>% 
    select(group, word_1, freq_2, freq_zipf_2, nd, global_similarity, lv) %>% 
    group_by(group) %>% 
    summarise_at(
        vars(freq_2:lv), 
        list(
            median = ~median(., na.rm = TRUE),  
            sd = ~sd(., na.rm = TRUE)
        )
    ) %>%
    gt(rowname_col = "group") %>% 
    tab_header(
        title = md("Table 1"),
        subtitle = md("Lexical frequency, phonological neigbourhood size, and levenshtein distance of the stimuli words.")
    ) %>% 
    tab_source_note(
        md("*Note*. Median and standard deviation (*SD*) of lexical frequencies of target words (expressed in counts per million and as Zipf scores), density of higher-frequency phonological neighbourhoods of target words, and normalised Levenshtein phonological similarity between the presented and the target words.")
    ) %>% 
    fmt_number(freq_2_median:nd_sd) %>%
    fmt_percent(matches("lv|global")) %>% 
    tab_spanner(
        md("**Freq. (million)**"),
        c("freq_2_median", "freq_2_sd", "freq_zipf_2_median", "freq_zipf_2_sd")
    ) %>% 
    tab_spanner(
        md("**Freq. (Zipf)**"), 
        matches("freq_zipf_2")
    ) %>% 
    tab_spanner(
        md("***PTHN* (presented)**"),
        matches("nd")
    ) %>% 
    tab_spanner(
        md("**Glob. similarity**"),
        matches("global")
    ) %>% 
    tab_spanner(
        md("**Levenshtein**"),
        matches("lv")
    ) %>% 
    cols_label(
        freq_2_median = md("Median"),
        freq_2_sd = md("*SD*"),
        freq_zipf_2_median = md("Median"),
        freq_zipf_2_sd = md("*SD*"),
        nd_median = md("Median"),
        nd_sd = md("*SD*"),
        global_similarity_median = md("*Mean*"),
        global_similarity_sd = md("*SD*"),
        lv_median = md("Median"),
        lv_sd = md("*SD*")
    ) %>% 
    summary_rows(
        columns = c(matches("median"), -matches("lv")),
        fns = list(
            Median = "median",
            SD = "sd"
        )
    ) %>% 
    summary_rows(
        columns = matches("lv"),
        fns = list(
            Median = "median",
            SD = "sd"
        ), 
        formatter = fmt_percent
    ) %>% 
    tab_style(
        style = cell_text(align = "left", weight = "bold", size = "medium"),
        locations = cells_title(groups = "title")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium", style = "italic"),
        locations = cells_title(groups = "subtitle")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_source_notes()
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_stub_grand_summary()
    ) %>% 
    tab_style(
        style = cell_borders(sides = c("left", "right"), color = "white"),
        locations = list(
            cells_body(),
            cells_row_groups(),
            cells_column_spanners(), 
            cells_stub(),
            cells_stub_grand_summary(), 
            cells_source_notes(),
            cells_column_labels(),
            cells_stubhead()
        )
    ) %>% 
    tab_style(
        style = list(
            cell_text(align = "left", size = "medium"),
            cell_borders(sides = "all", color = "white")
        ),
        locations = cells_stub()
    ) %>% 
    tab_style(
        style = cell_text(
            align = "center", 
            size = "medium",
            weight = "normal",
            style = "normal"
        ),
        locations = list(
            cells_column_spanners(),
            cells_column_labels()
        )
    ) %>% 
    tab_style(
        style = cell_borders(sides = "all", color = "white"),
        locations = cells_body(columns = 1:11)
    ) %>% 
    tab_style(
        style = cell_borders(sides = "top", color = "white"),
        locations = cells_body(columns = 1:11)
    ) %>% 
    as_raw_html()

@@

```{r stimuli-frequency, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
    distinct(
        group,
        word_1,
        .keep_all = TRUE
    ) %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(test_language = paste0(group,  " (N = ", n_total, ")")) %>% 
    ggplot(
        aes(
            freq_zipf_2, 
            fill = group
        )
    ) +
    facet_wrap(
        ~group, 
        ncol = 1
    ) +
    geom_histogram(
        bins = 25,
        colour = "white"
    ) +
    labs(
        x = "Lexical frequency (Zipf score)\nExtracted from CLEARPOND database", 
        y = "# trials", 
        fill = "Group"
    )  +
    scale_y_continuous(breaks = seq(0, 12, 2)) +
    theme(
        legend.position = "none",
        panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")
    )

@@

```{r stimuli-pthn, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(translation = paste0(word_1, "/", word_2)) %>% 
    ggplot() +
    facet_wrap(~group, scales = "free_y") +
    aes(
        x = nd, 
        y = reorder(translation, nd),
        colour = group,
        fill = group,
        label = translation
    ) + 
    geom_text(
        size = 3,
        hjust = 0
    ) +
    labs(
        x = "Group", 
        y = "# phonological neighbours", 
    ) +
    scale_x_continuous(breaks = seq(0, 30, 5)) +
    theme(
        legend.position = "none",
        panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()
    )

@@

```{r stimuli-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
    left_join(count(., group, name = "n_total")) %>% 
    mutate(group = paste0(group,  " (N = ", n_total, ")")) %>% 
    ggplot() +
    aes(
        x = lv,
        y = reorder_within(translation, lv, group),
        fill = group,
        colour = group,
        label = percent(lv, accuracy = 0.1)
    ) +
    facet_wrap(~group, scales = "free_y") +
    geom_text(
        size = 3,
        hjust = 0
    ) +
    labs(
        x = "Group", 
        y = "Phonological Leveshtein distance\n(corrected for string length)",
        fill = "Test language"
    ) +
    scale_x_continuous(
        labels = percent
    ) +
    scale_y_reordered() +
    theme(
        legend.position = "none",
        axis.title.y = element_blank(),
        axis.text.y = element_text(size = 7, hjust = 1),
        panel.grid.major.x = element_line(
            colour = "grey",
            linetype = "dotted"
        )
    ) 
ggsave(here("img", "lv.png"), height = 12)

@@

## Global similarity

```{r global-similarity, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
stimuli %>% 
    ggplot() +
    aes(
        x = global_similarity, 
        y = reorder_within(translation, global_similarity, group),
        label = percent(global_similarity, accuracy = 0.1),
        fill = group,
        colour = group,
    ) + 
    facet_wrap(~group, scales = "free_y") + 
    geom_text(
        size = 2,
        hjust = 0
    ) +
    labs(
        x = "Global similarity (mean)",
        y = "Translation"
    ) +
    scale_y_reordered() +
    scale_x_continuous(
        limits = c(0, 0.2),
        labels = percent
    ) +
    theme(
        legend.position = "none",
        axis.text.y = element_text(size = 7, hjust = 1),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_line(
            colour = "grey",
            linetype = "dotted"
        )
    )

ggsave(here("img", "global_similarity.png"), height = 12)
```

@@

medians <- stimuli %>% 
    select(group, word_1, freq_2, freq_zipf_2, nd, global_similarity, lv) %>% 
    group_by(group) %>% 
    summarise_at(
        vars(freq_2:lv), 
        list(
            median = ~median(., na.rm = TRUE),  
            sd = ~sd(., na.rm = TRUE)
        )
    )

# frequency
stimuli %>% 
    ggplot() + 
    aes(
        x = freq_zipf_2,
        fill = group
    ) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(
            xmin = freq_zipf_2_median-freq_zipf_2_sd,
            xmax = freq_zipf_2_median+freq_zipf_2_sd, 
            ymin = -Inf,
            ymax = Inf, 
            fill = group
        ),
        inherit.aes = FALSE,
        alpha = 0.15
    ) +   
    geom_histogram(
        bins = 20,
        colour = "white"
    ) +
    geom_vline(
        data = medians, 
        aes(
            xintercept = freq_zipf_2_median,
            group = group
        ), 
        colour = "black",
        size = 0.5,
        linetype = "dashed"
    ) + 
    geom_text(
        data = medians, 
        aes(
            label = "Median ± SD", 
            x = freq_zipf_2_median+1.25,
            y = 13
        ), 
        size = 3
    ) +
    geom_curve(
        data = medians, 
        aes(
            x = freq_zipf_2_median+0.85, 
            xend = freq_zipf_2_median+0.1,
            y = 12, 
            yend = 11
        ),
        arrow = arrow(length = unit(0.2, "cm")),
        curvature = -0.25,
        colour = "grey30"
    ) +
    labs(
        x = "Lexical frequency (Zipf)", 
        y = "Number of trials", 
        title = "Frequency\n(stimuli translations)\n"
    ) +

    # PTHN 1
    stimuli %>% 
    count(group, nd) %>% 
    ggplot(
        aes(
            x = nd, 
            y = n,
            fill = group
        )
    ) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(
            xmin = 0, 
            xmax = nd_median+nd_sd, 
            ymin = -Inf, 
            ymax = Inf,
            fill = group
        ), 
        inherit.aes = FALSE, 
        alpha = 0.15
    ) +   
    geom_col(colour = "white") + 
    geom_vline(
        data = medians, 
        aes(
            xintercept = nd_median,
            group = group
        ), 
        colour = "black", 
        size = 0.5,
        linetype = "dashed"
    ) + 
    labs(
        x = "PTHN across languages", 
        y = "Number of trials", 
        title = "Higher-frequency neighbours\n(stimuli translations)\n"
    ) +

    # global similarity
    stimuli %>% 
    ggplot(
        aes(
            x = global_similarity, 
            fill = group
        )
    ) + 
    facet_wrap(~group, ncol = 1) + 
    geom_rect(
        data = medians, 
        aes(
            xmin = 0, 
            xmax = global_similarity_median+global_similarity_sd, 
            ymin = -Inf, 
            ymax = Inf,
            fill = group
        ), 
        inherit.aes = FALSE, 
        alpha = 0.15
    ) +   
    geom_histogram(colour = "white") + 
    geom_vline(
        data = medians, 
        aes(
            xintercept = global_similarity_median,
            group = group
        ), 
        colour = "black", 
        size = 0.5,
        linetype = "dashed"
    ) + 
    labs(
        x = "Global similarity across languages", 
        y = "Number of trials", 
        title = "Mean cross-language similarity\n(stimuli translations)\n"
    ) +

@@

    plot_layout(
        guides = "collect",
        nrow = 1
    ) &
    plot_annotation(tag_levels = "A") &
    scale_fill_manual(
        values = c("#1A85FF", "#ff2976", "#FFC20A"), 
        na.translate = FALSE
    ) &
    theme(legend.position = "none")

@@

participants_coded %>% 
    filter(valid_participant=="Valid") %>% 
    select(
        participant_id, 
        group, 
        n,
        n_valid
    ) %>%
    mutate(valid_prop = n_valid/n) %>% 
    ggplot() +
    aes(
        x = valid_prop, 
        fill = group,
        colour = group
    ) + 
    facet_wrap(~group) +
    geom_histogram() +
    labs(
        x = "Valid trials (%)",
        y = "N participants",
        fill = "Group",
        colour = "Group"
    ) +
    scale_x_continuous(labels = percent) +
    theme(
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank(),
        panel.grid.major.y = element_line(
            linetype = "dotted", 
            colour = "grey"
        )
    )
```

@@

participants_valid %>% 
    count(group, l2, .drop = FALSE) %>% 
    mutate(
        l2 = case_when(
            l2=="Alemã\u0081n" ~ "German",
            l2=="Francã\u2030s" ~ "French",
            l2=="Cuã\u0081l" ~ "Missing",
            TRUE ~ l2
        ),
    ) %>% 
    left_join(
        count(
            participants_valid, 
            group, 
            name = "n_total"
        )
    ) %>% 
    mutate(group = paste0(group,  "\n(N = ", n_total, ")")) %>% 
    ggplot() +
    aes(
        group,
        n,
        fill = l2
    ) + 
    facet_wrap(
        ~group, 
        ncol = 1,
        scales = "free_y"
    ) +
    geom_col(position = position_fill()) +
    labs(
        x = "L2", 
        y = "# participants", 
        fill = "L2"
    ) +
    scale_y_continuous(labels = percent) +
    coord_flip() +
    theme(
        legend.position = "top",
        legend.title = element_blank(),
        strip.text = element_blank(),
        panel.grid = element_blank(),
        axis.text.x = element_text(),
        axis.title.y = element_blank()
    )

@@

```{r responses_coded, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
responses_coded <- responses %>% 
    # typos are considered correct responses
    mutate_at(vars(group), as.factor) %>% 
    # center predictors
    mutate_at(
        vars(lv_std, nd_std, freq_zipf_2_std),
        function(x) scale(x, center = TRUE, scale = TRUE)[,1]) %>% 
    # impute missing data
    as_tibble() %>% 
    arrange(group, word)
```

@@

model_loos_gs %>% 
    as.data.frame() %>% 
    rownames_to_column("model") %>% 
    arrange(desc(elpd_loo)) %>% 
    select(
        model,
        matches("elpd_loo"),
        matches("looic"),
        matches("diff")
    ) %>%
    mutate(model = str_replace(model, "fit_", "Model ")) %>% 
    mutate_all(~ifelse(. == 0, NA, .)) %>% 
    gt(rowname_col = "model") %>% 
    tab_header(
        title = md("Table 2"),
        subtitle = md("Model performance and comparison using leave-one-out cross-validation")
    ) %>% 
    tab_source_note(
        md("*Note*. Outcomes of the leave-one-out cross-validation procedure. Each row indicates the values of the expected log-predicted density (*ELPD*), leave-one-out information creterion (*LOO-IC*), and the difference in *ELPD* (*LOO-diff*) between each model and the inmediately simpler model. Each value is accompanied by a standard error (*SE*) indicating the uncertainty of its estimate.")
    ) %>% 
    fmt_missing(everything(), missing_text = "-") %>% 
    fmt_number(2:7) %>% 
    cols_label(
        model = md("**Model**"),
        looic = md("***LOO<sub>IC</sub>***"),
        se_looic = md("***SE*<sub>IC</sub>**"),
        elpd_loo = md("***LOO<sub>ELPD</sub>***"),
        se_elpd_loo = md("***SE***"),
        elpd_diff = md("***LOO<sub>diff</sub>***"),
        se_diff = md("***SE<sub>diff</sub>***")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", weight = "bold", size = "medium"),
        locations = cells_title(groups = "title")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium", style = "italic"),
        locations = cells_title(groups = "subtitle")
    ) %>% 
    tab_style(
        style = cell_text(align = "left", size = "medium"),
        locations = cells_source_notes()
    ) %>% 
    tab_style(
        style = list(
            cell_borders(
                sides = c("left", "right"), 
                color = "white"
            ),
            cell_text(
                align = "center"
            )
        ),
        locations = list(
            cells_body(), 
            cells_row_groups(), 
            cells_column_spanners(), 
            cells_stub(),
            cells_source_notes(),
            cells_column_labels(),
            cells_stubhead()
        )
    ) %>% 
    tab_style(
        style = list(
            cell_text(align = "left", size = "medium"), 
            cell_borders(sides = "all", color = "white")
        ),
        locations = list(
            cells_stub(), 
            cells_source_notes()
        )
    ) %>% 
    tab_style(
        style = cell_text(
            align = "center", 
            size = "medium",
            weight = "normal",
            style = "normal"
        ),
        locations = list(
            cells_column_spanners(),
            cells_column_labels()
        )
    ) %>% 
    tab_style(
        style = cell_borders(sides = "all", color = "white"),
        locations = cells_body(columns = 1:7)
    ) %>% 
    tab_style(
        style = cell_borders(sides = "top", color = "white"),
        locations = cells_body(columns = 1:7)
    ) %>% 
    as_raw_html()

@@

coefs <- fixef(fit_4_gs) %>% 
    as.data.frame() %>% 
    rownames_to_column("variable") %>% 
    clean_names() %>% 
    mutate_at(
        vars(estimate:q97_5), 
        ~ifelse(
            variable=="Intercept",
            inv_logit_scaled(.),
            ./4
        )
    )

str_repl <- c(
    "Intercept" = "Intercept",
    "freq_zipf_2_std" = "Frequency\n[+1 SD]",
    "global_similarity_std:lv_std" = "Glob. similarity \u00d7 Levenshtein", 
    "global_similarity_std" = "Glob. similarity \n[+1 SD]",
    "lv_std" = "Levenshtein\n[+1 SD]"
)

coefs %>% 
    mutate(
        variable = str_remove(variable, "b_") %>% 
            str_replace_all(str_repl) %>% 
            factor(
                levels = c(
                    "Intercept", 
                    "Frequency\n[+1 SD]", 
                    "Glob. similarity \n[+1 SD]", 
                    "Levenshtein\n[+1 SD]",
                    "Glob. similarity \u00d7 Levenshtein"
                )
            )
    ) %>% 
    select(-est_error) %>% 
    gt() %>% 
    fmt_percent(2:4) %>% 
    cols_merge(
        c("q2_5", "q97_5"), 
        pattern = "[{1}, {2}]"
    ) %>% 
    cols_label(
        variable = md("**Predictor**"),
        estimate = md("**Mean**"),
        q2_5 = md("**95\\% CrI**"),
    ) %>% 
    tab_source_note("Estimated posterior distributions of coefficients in Model 6. A\\) Population-level effects. Distributions indicate the estimated posterior likelihood density of regression coefficients of fixed effects. Credible intervals (*CrI*), represented with increasingly lighter segmentents in the distribution indicate the range of values that contain the true value with 95\\%, 80\\%, and 50\\% probability. Black dots represent the mean of each distribution.") %>% 
    cols_align(align = "left") %>% 
    as_raw_html()
```
